The pollination trade-off

### 2018-12-09 paper/manuscript.Rmd
Minor edits to discussion

\R{disc-facil-comp}Both of the tests used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.

@@

Simultaneously, because visitation, pollen production and abundance are correlated, the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition. 
The relative wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].

The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be benetitial to both the quantity and quality of pollination.
Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
This does not necessarily implies that these variables are unimportant to pollen deposition. 
Instead, it is also possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref). 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Alternatively, other factors that we were unable to meassure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service. 
\R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 
First, in the models of pollen deposition, the random structure that allowed plants of the same species to have different intercepts across communities was much better supported by the data than the structure that fixed the intercept for a plant species irrespective of the community. 
Second, in a large majority of cases, the strategies that a species uses across communities are not more similar to each other than what would be expected at random. 
Lit? Context?
On the one hand these two variables are more tighly related to the understanding of competition at the community scale than metrics of dominance. 
On the other, having distinct traits, for example trough phenology differentiation, has a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities [@ye_competition_2014]. 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Similarly, other factors, not meassured in our study, like pollinator behaviour and densities [@ye_competition_2014; ref to Melissa's paper?] or the spatial context [@cariveau_spatially_2009] can also shape the way sharing pollinators affects the pollination service.

>>>>

\R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.

@@

Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition. 
The relative wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].

The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be benetitial to both the quantity and quality of pollination.
Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
This does not necessarily implies that these variables are unimportant to pollen deposition. 
Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref). 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Alternatively, other factors that we were unable to meassure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service. 
\R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 
First, in the models of pollen deposition, the random structure that allowed plants of the same species to have different intercepts across communities was much better supported by the data than the structure that fixed the intercept for a plant species irrespective of the community. 
Second, in a large majority of cases, the strategies that a species uses across communities are not more similar to each other than what would be expected at random. 
Lit? Context?
On the one hand these two variables are more tighly related to the understanding of competition at the community scale than metrics of dominance. 
On the other, having distinct traits, for example trough phenology differentiation, has a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities [@ye_competition_2014]. 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Similarly, other factors, not meassured in our study, like pollinator behaviour and densities [@ye_competition_2014; ref to Melissa's paper?] or the spatial context [@cariveau_spatially_2009] can also shape the way sharing pollinators affects the pollination service.
